### 2022-08-11 main/chapter_2ljets.tex
begin unblinding proofread

Blindness to data is useful, but not necessary.
All that is necessary is that our predictions are independent of the data
they are supposed to predict.
Probabilistically, that independence makes our Poisson likelihood assignments
justifiable, and scientifically it allows our modelling to be useful if it
makes accurate predictions.
If one knows what the data are, then it takes utter honesty ---
Feynman's ``leaning over backwards''~\cite{feynman1974cargo} ---
to assign predictions as if the data were unknown.
Blindness is a useful and wilful ignorance that automatically implements this
honesty without this backbreaking work.

>>>>

Blindness to data is useful, but not necessary ---
all that is necessary is that our predictions are independent of the data
they are supposed to predict.
Probabilistically, that independence makes our Poisson likelihood assignments
justifiable, and scientifically it allows our modelling to be useful if it
makes good predictions.
If one knows what the data are, then it takes utter honesty ---
Feynman's ``leaning over backwards''~\cite{feynman1974cargo} ---
to assign predictions as if those data were not known.
Blindness is therefore a useful, wilful ignorance that automatically implements
this honesty without the (backbreaking) mental work of acting ``as if'' blind.
